Sequential Composition for Relaxed Memory: Pomsets with Predicate Transformers

### 2021-04-17 paper/outro.tex
fleshed out merge
Fleshed out outro

\citet{DBLP:conf/esop/PaviottiCPWOB20} use step-indexing to account for
loops; we expect that the same approach could be applied here.

>>>>

This paper is the first to present a compositional semantics for
sequential composition in a relaxed memory model which can be
efficiently compiled to modern CPUs. There is, as usual, more research
to be done.

We have not treated loops in this model, though we expect that the usual
approach of showing continuity for all the semantic operations with respect to set inclusion
would go through. \citet{DBLP:conf/esop/PaviottiCPWOB20} use step-indexing to account for
loops; a similar approach could be applied here.

In \S\ref{sec:arm1} we presented a compilation strategy to \armeight{}
for a simplified model, but which introduces fences to acquiring
reads. These fences are not required in \S\ref{sec:arm2}, but at the
cost of model complexity. It would be illuminating to find out what
the performance penalty is for these fences.

An earlier version of this paper has been mechanized in Agda; it would be
reassuring to update the mechanization to bring it in line with the current state.
